%max 2 pages:
%\begin{itemize}
%\item Description of problem area and problem itself
%\item What is the research question/goal?
%\item Why is this is an important/meaningful/interesting problem to consider?
%\item the very basic idea of the approach and why is this a reasonable approach for this problem?
%\end{itemize}

Online music services consist of large databases of meta-data for songs and artists, which are used to suggest artists to users based on their earlier listening habits. However, most of the information on such websites is crowd sourced and thus error-prone. Moreover, obscure artists and releases are often unlabeled. The main problem with manual labeling is that the process costs both time and money.  Consequently, automated classification of music genres would provide music services with a cost efficient way of labeling. Furthermore, a generative model approach may provide new insight into the themes present in different music genres that elude casual fans.

Music genre classification has been researched mostly using audio signals\cite{audio_classification}. While this approach uses the \textit{defining} characteristic of most music genres, namely their musical structure, an other approach is to use word-based analysis, which has the advantage of smaller datasets, since text files are smaller than audio files. Some earlier research has been done in the field by classifying songs using their lyrics, but often different lyric-features like syntactic structure\cite{felllyrics}, the amount of words per minute and the average word length\cite{mayeraudiolyrics}, recognition of structures in the lyrics\cite{maxwellgenome} or a combination of audio signals and lyrics\cite{mayeraudiolyrics} have been used. Little research has been done on classifying song using only the words of the lyrics\cite{stateoftheart}, with topic models using Gibbs sampling. Other research has used LDA for artist assignment instead of genre classification\cite{liartists}, however, this research took audio features into account as well. However, since different music genres tend to deal with different themes and thus lyrics, can an extension of LDA over music genres instead of documents be used to classify music genres?

This paper proposes that extending LDA over genres instead of documents may prove useful in classifying music into genres. In order to classify data using this new model, a dataset was built, since there are no such datasets readily available. To achieve this, a crawler was written to automatically retrieve documents and labels. After building the dataset, it was cleaned and split into a training set and a test set (using 5-fold cross-validation). When running the algorithm, the topics were randomly initialized and Gibbs sampling was run for a set number of iterations. After this, the topic distribution for each genre from the test set was calculated to build a genre profile, and these profiles were used to train an SVM to predict the most probable genre of a new document.

The complete outline of the problem can be found in section \ref{sec:problem}, a detailed description of the approach used can be found in section \ref{sec:approach} and the results of this approach can be found in section \ref{sec:experiment}. The conclusions and discussion can be found in section \ref{sec:discussion} and the team responsibilities in section \ref{sec:team}.